\documentclass{resume}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\def\-{\discretionary{}{}{}}

\author{Nicholas J. Tustison}
% ------ Address --------------------------------------------------------

\address{University of Virginia\\
    Department of Radiology and Medical Imaging\\
    
%    University of Pennsylvania \\
%    3600 Market Street \\
%    Suite 320\\
%    Philadelphia, PA  19104\\
%    (610) 308-1211 \\
%    ntustison@wustl.edu \\
%    \mbox{\small\tt ntustison@wustl.edu}\\
%    \mbox{\small\tt http://www.cs.yale.edu/homes/csuros-miklos/}}{ 
%    3600 Market Street\\
%    Suite 320\\ 
%    New Haven, CT 06511\\
%    (203) 865-2145}
    
    }


\begin{document}
\maketitle

% ------- Education ---------------------------------------------------

\begin{category}{Education}
   \citem{University of Pennsylvania}, Philadelphia, PA.\\
      Post-doctoral fellowship, September 2005.
   \citem{Washington University in St. Louis}, St. Louis, MO.\\
      D.Sc. in Biomedical Engineering, August 2004.\\
      Thesis title: {\em Biventricular Myocardial Strains With Anatomical NURBS Models From Tagged MRI.}
   \citem{University of Virginia}, Charlottesville, VA. \\
      M.S. in Biomedical Engineering, May 2000.\\
      Thesis title: {\em Quantification Methods for Assessing Asthma
                         in Hyperpolarized $^3$He Lung MRI Studies.}
   \citem{Brigham Young University}, Provo, UT. \\
      B.S. in Applied Physics: Computer Science Emphasis, April 1998.\\
      Minor: Mathematics
   \citem{Scholarships}
   \begin{itemize}
      \item UVa School of Engineering merit award
      \item UVa Biomedical Engineering merit award
      \item BYU Trustees Scholarship (Full tuition--4 years)
   \end{itemize}
\end{category}

% -------- Work experience --------------------------------------------

\begin{category}{Work experience}
\citem{Assistant Professor}, Department of Radiology and Medical Imaging, University of Virginia (July 2010--present)
\citem{Senior Research Investigator}, Penn Image Computing and Science Laboratory, Radiology Department, University of Pennsylvania (September 2005--July 2010)
\citem{Research Fellow}, Penn Image Computing and Science Laboratory, Radiology Department, 
                         University of Pennsylvania (August 2004--September 2005)
\citem{Research Assistant}, Cardiovascular Image Analysis Laboratory, Washington University
                           in St. Louis (August 2000--August 2004)
\citem{Research Assistant}, Radiology Department, University of Virginia Health
                            Sciences Center (May 1998--June 2000)
\citem{Teaching Assistant}, Physics Department, Brigham Young University (September
                            1996--May 1998)
\citem{Teaching Assistant}, Math Department, Utah Valley State College
                            (May 1996--May 1997)
\end{category}

% --------- Research ----------------------------------------------------

\begin{category}{Research interests}
   \citemnobullet
     digital topology, image registration and segmentation, open source software, translational research
\end{category}

% ------- Skills ------------------------------------------------------

\begin{category}{Skills}
\citemnobullet C/C++, Insight Toolkit, Paraview, perl, Visualization Toolkit, Matlab, R
%\citembullet Fluent: Spanish
\end{category}

% ------- Program committees------------------------------------------------------

\begin{category}{Program Committees}
\citemnobullet SPIE Medical Imaging 2012--
\end{category}

% ------- Editorial boards ------------------------------------------------------

\begin{category}{Editorships}
\citemnobullet Frontiers Review Editorial Board May 2012--
\end{category}

% ------- Reviewer Duties------------------------------------------------------

\begin{category}{Reviewer Duties}
\citemnobullet Academic Radiology
\citemnobullet Annals of Biomedical Engineering
\citemnobullet Computers in Biology and Medicine
\citemnobullet Focused Ultrasound Foundation ad hoc grant reviewer
\citemnobullet Image and Vision Computing
\citemnobullet International Journal of Pattern Recognition and Artificial Intelligence	
\citemnobullet IEEE Transactions on Medical Imaging
\citemnobullet IEEE Transactions on Pattern Analysis and Machine Intelligence
\citemnobullet IEEE Transactions on Biomedical Engineering
\citemnobullet Insight Journal
\citemnobullet International Conference on Medical Image Computing and Computer Assisted Intervention
\citemnobullet International Journal of Biomedical Imaging
\citemnobullet International Journal of Computer Vision
\citemnobullet International Workshop on Medical Imaging and Augmented Reality
\citemnobullet IEEE International Symposium on Biomedical Imaging:  From Nano to Macro
\citemnobullet Journal of Computed Tomography
\citemnobullet Journal of Electronic Imaging
\citemnobullet Journal of Magnetic Resonance Imaging
\citemnobullet Journal of Neurotrauma
\citemnobullet Journal of the Optical Society of America A
\citemnobullet Magnetic Resonance in Medicine
\citemnobullet Medical Physics
\citemnobullet Medical Image Analysis
\citemnobullet Neuroradiology
\citemnobullet Respirology
\end{category}


% -------- Publication --------------------------------------------

\begin{category}{Research}
   \citemnobullet{\bf Journal Manuscripts}
   \begin{itemize}
    \citemnobullet Tustison NJ, Johnson H, Rohlfing T, Klein A, Ghosh S, Ibanez L, Avants BB: Instrumentation bias in the use and evaluation of scientific software: Recommendations for reproducible practices in the computational sciences, {\em Frontiers in Neuroscience}, 7(162).
    \citemnobullet Tustison NJ, Contrella B, Altes TA, Avants BB, de Lange EE, Mugler III JP: Voxel-based Longitudinal Analysis of Pulmonary Ventilation MRI, {\em Journal of Magnetic Resonance Imaging}, submitted.
    \citemnobullet Tustison NJ, Avants BB, Cook PA, Kim J, Whyte J, Gee JC, Stone JR: Logical Circularity in Voxel-Based Analysis:  normalization strategy may induce statistical bias, {\em Human Brain Mapping}, accepted.
    \citemnobullet Song G, Barbosa JR EM, Tustison NJ, Gefter WB, Kreider M, Gee JC, Torigian DA: A Comparative Study of HRCT Image Metrics and PFT Values for Characterization of ILD and COPD, {\em Academic Radiology}, 19(7):857--64, July 2012.
    \citemnobullet Yilmaz C, Tustison NJ, Dane DM, Ravikumar P, Takahashi M, Gee JC, Hsia CCW:  Functional computed tomography:  Progressive adaptation in regional mechanics following extensive lung resection, {\em Journal of Applied Physiology}, 111(4):1150--8, October 2011.
    \citemnobullet Avants BB$^*$, Tustison NJ$^*$, Wu J, Cook PA, Gee JC:  An Open Source Framework for $n$-Tissue Segmentation with Evaluation on Public Data, {\em Neuroinformatics}, 9(4):381--400, December 2011.\\
    $^*$Joint first authorship.
    \citemnobullet Murphy K, van Ginneken B, Reinhardt JM, \ldots, Tustison NJ, \ldots, Pluim JPW:  Evaluation of Registration Methods on Thoracic CT:  The EMPIRE10 Challenge,  {\em IEEE Transactions on Medical Imaging}, 30(11):1901--20, November 2011.
    \citemnobullet Tustison NJ, Avants BB, Altes TA, de Lange EE, Mugler III JP, Gee JC:  Ventilation-Based Segmentation of the Lungs Using Hyperpolarized $^3$He MRI, {\em Journal of Magnetic Resonance Imaging}, 34(4):831--841, October 2011.
    \citemnobullet Barbosa Jr EM, Song G, Tustison N, Kreider M, Gee JC, Gefter W, Torigian DA:  Computational Analysis of Thoracic Multidetector Row HRCT for Segmentation and Quantification of Small Airway Air Trapping and Emphysema in Obstructive Pulmonary Disease, {\em Academic Radiology}, 18(10):1258-1269, October 2011.
    \citemnobullet Tustison NJ, Avants BB, Siqueira M, Gee JC:  Topological Well-Composedness and Glamorous Glue:  A Digital Gluing Algorithm for Topologically Constrained Level Set Segmentation, {\em IEEE Transactions on Image Processing}, 20(6):1756-1771, June 2011.
    \citemnobullet Tustison NJ, Cook TS, Song G, Gee JC:  Pulmonary Kinematics from Image Data---A Review, {\em Academic Radiology}, 18(4):402--417, April 2011.
    \citemnobullet Tustison NJ, Awate SP, Song G, Cook TS, Gee JC:  Point Set Registration Using Havrda-Charvat-Tsallis Entropy Measures. {\em IEEE Transactions on Medical Imaging}, 30(2):451--460, February 2011.
    \citemnobullet Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC:  A Reproducible Evaluation of ANTs Similarity Metric Performance in Brain Image Registration, {\em Neuroimage}, 54(3):2033--2044, February 2011.
    \citemnobullet Tustison NJ, Avants BB, Cook PA, Egan A, Zheng Y, Yushkevich PA, Gee JC:  N4ITK:  Improved N3 Bias Correction, {\em IEEE Transactions on Medical Imaging}, 29(6):1310--1320, June 2010.
    \citemnobullet Tustison NJ, Altes TA, Song G, de Lange EE, Mugler III JP, Gee JC:  Feature Analysis of Hyperpolarized Helium-3 Pulmonary MRI:  A Study of Asthmatics versus Non-Asthmatics, {\em Magnetic Resonance in Medicine}, 63(6):1448--1455, June 2010.
    \citemnobullet Tustison NJ, Awate SP, Cai J, Altes TA, Miller GW, de Lange EE, Mugler III JP, Gee JC:  Pulmonary Kinematics from Tagged Hyperpolarized Helium-3 MRI, {\em Journal of Magnetic Resonance Imaging}, 31(5):1236--1241, May 2010.
    \citemnobullet Tustison NJ, Avants BB, Gee JC: Directly manipulated free-form deformation image registration. {\em IEEE Transactions on Image Processing} 18(3):624--35, March 2009.
    \citemnobullet Siqueira M, Latecki LJ, Tustison N, Gallier J, Gee J: Topological Repairing of 3D Digital Images. {\em Journal of Mathematical Imaging and Vision} 30(3):249--274, March 2008.
    \citemnobullet Tustison NJ, Amini AA: Biventricular myocardial strains via nonrigid registration of anatomical NURBS model. {\em IEEE Transactions on Medical Imaging} 25(1):94--112, January 2006.
    \citemnobullet Tustison NJ, Amini AA: Myocardial kinematics from tagged MRI based on a 4-D B-spline model. {\em IEEE Transactions on Biomedical Engineering} 50(8):1038--1040, August 2003.
    \citemnobullet Hagspiel KD, Altes TA, Mugler III JP, Mata JF, Tustison NJ, Brookeman JR: MR virtual colonography using hyperpolarized $^3$He as an endoluminal contrast agent: demonstration of feasibility. {\em Magnetic Resonance in Medicine} 44(5):813, November 2000.
   \end{itemize}

% -------- Conferences --------------------------------------------

   \citemnobullet {\bf Conference Proceedings}
   \begin{itemize}
   \citemnobullet Durst C, Raghavan P, Tustison N, Patrie, J, Cupino A, Xin W, Wintermark M. Multiparametric Imaging Model to Accurately Predict Extent of Invasion of High-Grade Gliomas. ASNR Scientific Paper (Oral), 2013.
   \citemnobullet Tustison NJ, Muratore A, Contrella B, Mugler III JP, de Lange EE, and Altes TA:  
   In {\em Proceedings of the $21^{st}$ Voxelwise Comparison of Hyperpolarized He-3 and Xe-129 Lung Ventilation MR Imaging in Cystic Fibrosis.  Annual Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Salt Lake City, 2013.
   \citemnobullet Tustison NJ, Avants BB, Cook PA, Song G, Das S, van Strien N, Stone JR,
   Gee JC:  The ANTs Cortical Thickness Processing Pipeline.  
   In: {\em SPIE Medical Imaging: Biomedical Applications in Molecular, Structural, and 
   Functional Imaging}. Orlando 2013.
   \citemnobullet Tustison NJ, Contrella B, Altes TA, Avants BB, de Lange EE, Mugler III JP:  
   Longitudinal assessment of treatment effects on pulmonary ventilation using 1H/3He MRI 
   multivariate templates.
   In: {\em SPIE Medical Imaging: Biomedical Applications in Molecular, Structural, and 
   Functional Imaging}. Orlando 2013.
   \citemnobullet Tustison NJ, Avants BB, Cook PA, Gee JC, Stone JR:  
   Statistical Bias in Optimized VBM.
   In: {\em SPIE Medical Imaging: Biomedical Applications in Molecular, Structural, and 
   Functional Imaging}. Orlando 2013.
   \citemnobullet Tustison NJ, Avants BB:  Diffeomorphic Directly Manipulated Free-Form Deformation Image   
   Registration via Vector Field Flows.  In:  {\em Proceedings of the Workshop on Biomedical Image 
   Registration}.  Nashville 2012.
   \citemnobullet Avants BB, Tustison NJ, Song G, Wu B, Stauffer M, McCormick MM, Johnson HJ, Gee JC, Insight Software Consortium:  A Unified Image Registration Framework 
   for ITK4.  In:  {\em Proceedings of the Workshop on Biomedical Image 
   Registration}.  Nashville 2012.
   \citemnobullet Contrella B, Tustison NJ, Altes TA, Avants BB, Mugler III JP, de Lange EE: 
   4D segmentation and normalization of 3He MR images for intra-subject assessment of ventilated lung
   volumes. In: {\em SPIE Medical Imaging: Biomedical Applications in Molecular, Structural, and 
   Functional Imaging}. San Diego 2012.   
   \citemnobullet 
   Zheng Y, Keller B, Wang Y, Tustison N, Song G, Bakic PR, Maidment AD, Conant EF, Gee JC, Kontos D:
   A Fully-Automated Software Pipeline for Parenchymal Pattern Analysis in Digital Breast Images:
   Towards the Translation of Imaging Biomarkers in Routine Breast Cancer Risk Assessment.  In: 
   {\em The Quantitative Imaging Reading Room Showcase at RSNA 2011 Annual Meeting and Scientific Assembly}, 
   Chicago 2011.
   \citemnobullet Tustison NJ, Avants BB, Cook P, Kim J, Whyte J, Gee JC, Ahlers S, Stone J:  Multivariate
   Analysis of Diffusion Tensor Imaging and Cortical Thickness Maps in a Traumatic Brain Injury (TBI)
   Cohort Using Advanced Normalization Tools (ANTs).  In: {\em Proceedings of the 2011 
   annual meeting of the National Neurotrauma Society}, Fort Lauderdale, 2011.
   \citemnobullet Qing K, Altes TA, Tustison NJ, Mata JF, Miller GW, de Lange EE, Tobias WA, Cates GD, Brookeman JR,
   Mugler JP:  Acquisition of Spatially-registered Helium-3 and Proton 3D Image Sets of the Lung in less than 10 seconds using Compressed Sensing.  In {\em Proceedings of the $19^{th}$ Annual Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Montreal, 2011.
   \citemnobullet Tustison NJ, Avants BB, Flors L, Altes TA, de Lange EE, Mugler II JP, Gee JC: Segmentation of Lung Ventilation Defects Using Hyperpolarized $^3$He MRI.  In:  {\em Proceedings of the 2011 International Functional Pulmonary Imaging Workshop}, Philadelphia, 2011.
   \citemnobullet Tustison NJ, Avants BB, Flors L, Altes TA, de Lange EE, Mugler II JP, Gee JC: Ventilation-Based Segmentation of the Lungs Using Hyperpolarized Helium-3 MRI.  In:  {\em Joint Meeting combining The 3rd meeting of the Japanese Society of Pulmonary Functional Imaging and 5th International Workshop for Pulmonary  Functional  Imaging}, Hyogo, 2011.
    \citemnobullet Hsia CCW, Yilmaz C, Tustison NJ, Dane DM, Ravikumark P, Takahashi M, Gee JC:  Non-invasive measurement of regional mechanical strain and shear following extensive lung resection by high-resolution computed tomography (HRCT).  In: {\em Proceedings of the American Thoracic Society International Conference}, Denver, 2011.
    \citemnobullet Song G, Tustison NJ, Avants BB, Gee JC:  Lung CT Image Registration Using Diffeomorphic Transformation Models. In: {Proceedings of the Evaluation of Methods for Pulmonary Image Registration (EMPIRE) Grand Challenge organized by the 13th International Conference on Medical Image Computing and Computer Assisted Intervention}, Beijing, 2010.
    \citemnobullet Tustison NJ, Avants BB, Altes TA, Mugler II JP, Gee JC:  Automatic Segmentation of Ventilation Defects in Hyperpolarized 3He MRI.  In:  {\em Proceedings of the Annual Meeting of the Biomedical Engineering Society}, Austin, 2010.
    \citemnobullet Avants B, Cook PA, McMillan C, Grossman M, Tustison NJ, Zheng Y, Gee JC:  Sparse Unbiased Analysis of Anatomical Variance in Longitudinal Imaging.  In: {\em Proceedings of the Medical Image Computing and Computer Assisted Intervention Society (MICCAI)}, Beijing, 2010.
    \citemnobullet Avants B, Klein A, Tustison N, Woo J, Gee J:  Evaluation of an Open-Access, Automated Brain Extraction Method on Multi-Site Multi-Disorder Data. In:  {\em Proceedings of the $16^{th}$ Annual Meeting of the Organization for Human Brain Mapping (HBM)}, Barcelona, 2010.   
    \citemnobullet Wright AC, Yoder J, Tustison N, Gee J, Wehrli FW, Elliot DM:  High-Resolution MRI at 7T of Local Strains in the Intervertebral Disc. In:  {\em Proceedings of the $18^{th}$ Annual Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Stockholm, 2010.   
    \citemnobullet Tustison NJ, Altes TA, Miller GW, de Lange EE, Mugler JP, Gee JC: Retrospective Bias Correction of Hyperpolarized $^3$He MRI of the Lung. In:  {\em Proceedings of the $18^{th}$ Annual Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Stockholm, 2010.   
    \citemnobullet Tustison NJ, Altes TA, Song G, de Lange EE, Mugler JP, Gee JC: Hyperpolarized $^3$He Image Feature Analysis in Asthmatics. In:  {\em Proceedings of the $18^{th}$ Annual Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Stockholm, 2010.   
    \citemnobullet  Tustison NJ, Avants BB, Cook P, Gee J: N4ITK:  Improved N3 Bias Correction with Robust B-Spline Approximation. In:  {\em Proceedings of the $7^{th}$ Annual IEEE International Symposium on Biomedical Imaging: From Nano to Macro (ISBI)}, Rotterdam, 2010.
    \citemnobullet Tustison NJ, Altes TA, Song G, Mugler JP, de Lange EE, Gee JC: Feature Analysis of Hyperpolarized Helium-3 Pulmonary MRI in Asthmatics versus Non-Asthmatics. In: {\em Proceedings of the $2^{nd}$ International Workshop on Pulmonary Image Analysis}, London, 2009.
    \citemnobullet Cook TS, Tustison NJ, Song G, Awate SP, Torigian DA, Gefter W, Gee JC: Segmentation-Based Quantitation of Pulmonary Alveolar Proteinoisis, Pre- and Post-Lavage, Using High-Resolution Computed Tomography. In: {\em Proceedings of the $2^{nd}$ International Workshop on Pulmonary Image Analysis}, London, 2009.
    \citemnobullet Song G, Tustison NJ, Barbosa Jr E, Gee JC, Gefter W, Kreider M, Torigian DA: A Comparative Study of HRCT Image Metrics and PFT Values for Characterization of ILD and 
COPD. In: {\em Proceedings of the $2^{nd}$ International Workshop on Pulmonary Image Analysis}, London, 2009.
    \citemnobullet Tustison NJ, Awate SP, Song G, Cook T, Gee JC: A new information-theoretic measure to control the robustness-sensitivity trade-off for DMFFD point-set registration. In: {\em Proceedings of the 21$^{st}$ Biennial International Conference on Information Processing in Medical Imaging (IPMI)}, Williamsburg, 215--226, 2009.   
     \citemnobullet Cook T, Barbosa E, Tustison N, Song G, Torigian D, Koo C, Gefter W, Gee J: Quantitation of Pulmonary Alveolar Proteinosis, Pre- and Post-Lavage: A Feasibility Study. In: {\em Proceedings of the $2^{nd}$ World Congress of Thoracic Imaging and Diagnosis in Chest Disease}, Valencia, 2009.
     \citemnobullet Barbosa E, Song G, Tustison N, Torigian D, Kreider M, Koo C, Gefter W, Gee J: Computational Analysis of HRCT for characterization and differentiation of ILD and COPD. In: {\em Proceedings of the $2^{nd}$ World Congress of Thoracic Imaging and Diagnosis in Chest Disease}, Valencia, 2009.
    \citemnobullet  Song G, Barbosa E, Tustison N, Torigian D, Kreider M, Koo C, Gefter W, Gee J: Computational Analysis of HRCT Images For Characterization and Differentiation of ILD and COPD. In:  {\em Proceedings of the $6^{th}$ Annual IEEE International Symposium on Biomedical Imaging: From Nano to Macro (ISBI)}, Boston, 2009.
     \citemnobullet Tustison NJ, Kotzer CJ, Logan GA, Podolin PL, Altes TA, Wright AP, Song G, Zhao H, Haczku A,  Barnette MS, Panettieri Jr RA, Gee JC: Detection of elastase induced emphysema in free-breathing mice using micro computed tomography (CT). In:  {\em Proceedings of the Annual International Conference of the American Thoracic Society}, Toronto, 2008.
    \citemnobullet Tustison NJ, Cai J, Altes TA, Miller GW, de Lange EE, Mugler JP, Gee JC: Pulmonary Kinematics From 3-D Hyperpolarized Helium-3 Tagged Magnetic Resonance Imaging. In:  {\em Proceedings of the $16^{th}$ Annual Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Toronto, 2008.   
    \citemnobullet  Tustison N, Awate SP, Cai J, Altes T, Miller G, Lange E, Mugler J, Gee JC: Point-set registration of tagged He-3 images using a structurally-based Jensen-Shannon divergence measure within a deterministic-annealing framework. In:  {\em Proceedings of the $5^{th}$ Annual IEEE International Symposium on Biomedical Imaging: From Nano to Macro (ISBI)}, pp. 772--775, Paris, 2008.
    \citemnobullet    Tustison NJ, Altes TA, Gee JC, Cai J, de Lange EE, Mugler III JP: Pulmonary Kinematics From Hyperpolarized Helium-3 Tagged Magnetic Resonance Imaging. In: {\em Proceedings of the $4^{th}$ Annual IEEE International Symposium on Biomedical Imaging: From Nano to Macro (ISBI)}, pp. 368--371, Washington D.C., 2007.
    \citemnobullet  Cook TS, Tustison N, Biederer J, Tetzlaff R, Gee J: How do registration parameters affect quantitation of lung kinematics? In:  {\em Proceedings of the 10$^{th}$ International Conference on Medical Image Computing and Computer-Assisted Intervention (MICCAI)}, 10(Pt 1):817--24, 2007.
    \citemnobullet Tustison NJ, Avants BB, Gee JC: Improved FFD B-Spline Image Registration. {\em Proceedings of the $11^{th}$ Biennial IEEE International Conference on Computer Vision (ICCV)}, pp. 1--8, Rio de Janeiro, 2007.
    \citemnobullet  Tustison NJ, Gee, JC: Generalized $n$-D $C^k$ B-spline scattered data approximation with confidence values. {\em Proceedings of the $3^{rd}$ International Workshop on Medical Imaging and Augmented Reality (MIAR)}, pp. 76--83, Shanghai, 2006.
    \citemnobullet  Tustison NJ, Avants BB, Sundaram TA, Duda JT, Gee JC: A Generalization of Free-Form Deformation Image Registration Within the ITK Finite Element Framework. {\em Proceedings of the $3^{rd}$ International Workshop on Biomedical Image Registration (WBIR)}, pp. 238--246, Utrecht, 2006.
    \citemnobullet  Song Z, Tustison NJ, Avants BB, Gee JC: Adaptive graph cuts with tissue priors for brain MRI segmentation. In:  {\em Proceedings of the $3^{rd}$ Annual IEEE International Symposium on Biomedical Imaging: From Nano to Macro (ISBI)}, pp. 762--765, Arlington, 2006.
    \citemnobullet  Chen J, Tustison NJ, Amini AA: Accurate recovery of 4D left ventricular deformations using volumetric B-splines incorporating phase based displacement estimates. In: {\em Proceedings of SPIE:  Medical Imaging 2006:  Physiology, Function, and Structure from Medical Images}, 6143, San Diego, 2006.
    \citemnobullet  Tustison NJ, Amini AA: Comparison of parallel and spiral tagged MR imaging geometries in estimation of 3D myocardial strains. In: {\em Proceedings of SPIE:  Medical Imaging 2005:  Physiology, Function, and Structure from Medical Images}, 5746:571--579, San Diego, 2005.
    \citemnobullet  Tustison NJ, Amini AA: Lagrangian and Eulerian biventricular strains from anatomical NURBS models using tagged MRI. In: {\em Proceedings of SPIE:  Medical Imaging 2006:  Physiology, Function, and Structure from Medical Images},  5746:192--204, San Diego, 2005.
    \citemnobullet  Tustison, NJ, Abendschein D, Amini AA: Biventricular myocardial kinematics based on tagged MRI from anatomical NURBS models. In:  {\em Proceedings of the IEEE Computer Vision and Pattern Recognition (CVPR)}, 2:514, Quebec City, 2004.
    \citemnobullet  Tustison NJ, Amini AA: Myocardial Kinematics Based on Tagged MRI From Geometric Deformable Models. {\em Proceedings of SPIE:  Medical Imaging 2006:  Physiology, Function, and Structure from Medical Images}, 5369:22-33, San Diego, 2004.
    \citemnobullet  Tustison NJ, Amini AA: Tracking Myocardial Beads from SPAMM-MRI with a 4-D B-Spline Model. In:  {\em Proceedings of the 2$^{nd}$ Joint EMBS/BMES Conference}, pp. 993--994, Houston, 2002.
    \citemnobullet Tustison NJ, Abendschein D, Davila-Roman VG, Amini AA: Myocardial Strain Imaging with Tagged MRI. In: {\em Proceedings of the $16^{th}$ International Conference on Pattern Recognition (ICPR)}, 1:723--726, Quebec City, 2002.
    \citemnobullet Cooley B, Acton ST, Salerno M, Brookeman JR, Tustison NJ, de Lange EE, Altes TA: Automated Scoring of Hyperpolarized Helium-3 MR Lung Ventilation Images: Initial Development and Validation.  In:  {\em Proceedings of the $11^{th}$Annual  Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Honolulu, 2002.     
    \citemnobullet Tustison NJ, Yablonskiy D, Conradi M, Amini AA: Deformable Registration of 3HeMR and X-ray CT images of the lungs.  In:  {\em Proceedings of the $11^{th}$Annual  Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Honolulu, 2002.     
    \citemnobullet  Spellman MJ, Hagspiel KD, Altes TA, Mugler III JP, Mata JF, Tustison NJ, Brookeman JR: MR Virtual Colonoscopy using Hyperpolarized $^3$He as an Endoluminal Contrast Agent. In:  {\em Proceedings of the $8^{th}$Annual  Meeting of the International Society for Magnetic Resonance in Medicine (ISMRM)}, Philadelphia, 1999.            
   \end{itemize}

% -------- Book Chapters --------------------------------------------

   \citemnobullet {\bf Book Chapters}
   \begin{itemize}
   \citemnobullet Tustison NJ,  Amini AA: Analysis of 4-D Cardiac MR Data with NURBS Deformable Models:  Temporal Fitting Strategy and Nonrigid Registration. Parametric and Geometric Deformable Models:  An Application in Biomaterials and Medical Imagery. Jasjit S. Suri and Aly Farag (eds.). Springer Publishers, II, May 2007.
   \end{itemize}

% -------- Invited Talks --------------------------------------------

   \citemnobullet {\bf Invited Talks}
   \begin{itemize}
   \citemnobullet Stone JR, Tustison NJ:  Understanding the Inside of the Black Box: 
   Optimizing Approaches for the Analysis of Diffusion Tensor Imaging and Cortical Maps in TBI,
   {\em Keystone Symposia on Molecular and Cellular Biology}.  Keystone 2012.
   \citemnobullet Tustison NJ:  Open Source Software Tools for Lung Image Analysis, 
   {\em SPIE Medical Imaging: Biomedical Applications in Molecular, Structural, and 
   Functional Imaging}. San Diego 2012. 
   \end{itemize}

% -------- Other articles ------------------------------------------------------

   \citemnobullet {\bf Other Articles}
   \begin{itemize}
   \citemnobullet Tustison NJ: RGB Colormapping and ITK.  {\em The Source:  Kitware's Software Developer Quarterly}, January 2009, http://\-www\-.\-kitware\-.\-com/\-products/\-archive/\-kitware\_\-quarterly\-0709\-.pdf.
   \citemnobullet Tustison NJ: N4ITK:  Nick's N3 ITK Implementation for MRI Bias Field Correction.  {\em The Source:  Kitware's Software Developer Quarterly}, January 2010, http://\-www\-.\-kitware\-.\-com/\-products/\-archive/\-kitware\_\-quarterly\-0110\-.pdf.
   \end{itemize}

% -------- Open Source Software --------------------------------------------

   \citemnobullet {\bf Open Source Software}
   \begin{itemize} 
     \citemnobullet Tustison NJ, Avants BB:  The TVDMFFDVR Algorithm, {\em Insight Journal} 2012, http:\-//hdl\-.\-handle\-.\-net/10380/3334. 
     \citemnobullet Tustison NJ, Cook PA, Avants BB, Stone JR:  Simulated Diffusion-Weighted Imaging for the ITK Masses, {\em Insight Journal} 2011, http:\-//hdl\-.\-handle\-.\-net/10380/3315. 
   \citemnobullet  Tustison NJ, Avants BB, Siqueira M, Gee JC:  Escher's Ants as Metaphor: Topological Marching for the Well-Composed, Genus Zero Crowd, {\em Insight Journal} 2010, http:\-//hdl\-.\-handle\-.\-net/10380/3234. 
    \citemnobullet Tustison NJ, Gee JC:  Introducing Dice, Jaccard, and Other Label Overlap Measures To ITK, {\em Insight Journal} 2009, http:\-//hdl\-.\-handle\-.\-net/10380/3141.
    \citemnobullet Tustison NJ, Gee JC:  Introducing Dice, Jaccard, and Other Label Overlap Measures To ITK, {\em Insight Journal} 2009, http:\-//hdl\-.\-handle\-.\-net/10380/3141.
    \citemnobullet Yushkevich PA, Tustison NJ, Gee JC:  Gaussian Interpolation, {\em Insight Journal} 2009, http:\-//hdl\-.\-handle\-.\-net/10380/3139.
   \citemnobullet  Avants BB, Tustison NJ,  Song G: Advanced Normalization Tools v1.0,   {\em Insight Journal} 2009, http:\-//hdl\-.\-handle\-.\-net/10380/3113.  
   \citemnobullet  Tustison NJ,  Gee JC:  N4ITK:  Nick's N3 ITK Implementation for MRI Bias Field Correction,   {\em Insight Journal} 2009, http:\-//hdl\-.\-handle\-.\-net/10380/3053, Publication of the Month December 2009.  
   \citemnobullet  Tustison NJ,  Gee JC:  Stochastic Fractal Dimension Image,   {\em Insight Journal} 2009, http:\-//hdl\-.\-handle\-.\-net/1926/1525 ({\em accepted into the Insight Toolkit}), Publication of the Month April 2009.  
   \citemnobullet  Tustison NJ,  Awate SP, Gee JC:  Information-Theoretic Directly Manipulated Free-Form Deformation Labeled Point-Set Registration,   {\em Insight Journal} 2009, http:\-//hdl\-.\-handle\-.\-net/1926/1524.  
   \citemnobullet  Tustison NJ,  Yushkevich P, Gee JC:  Live-Wire-ing the Insight Toolkit with Intelligent Scissors,   {\em Insight Journal} 2008, http:\-//hdl\-.\-handle\-.\-net/1926/1372.  
   \citemnobullet  Tustison NJ,  Zhang H, Lehmann G, Yushkevich P, Gee JC: Meeting Andy Warhol Somewhere Over the Rainbow: RGB Colormapping and ITK,   {\em Insight Journal} 2008, http:\-//hdl\-.\-handle\-.\-net/1926/1452 ({\em accepted into the Insight Toolkit}).  
   \citemnobullet  Tustison NJ,  Gee JC:  Image Kernel Convolution,   {\em Insight Journal} 2008, http:\-//hdl\-.\-handle\-.\-net/1926/1323 ({\em accepted into the Insight Toolkit}).  
   \citemnobullet  Tustison NJ,  Yushkevich P, Song Z, Gee JC:  Graph Cuts, Caveat Utilitor, and Euler's Bridges of Konigsberg,   {\em Insight Journal} 2008, http:\-//hdl\-.\-handle\-.\-net/1926/1503, Publication of the Month December 2008.  
   \citemnobullet  Tustison NJ,  Gee JC,  Run-Length Matrices For Texture Analysis,   {\em Insight Journal} 2008, http:\-//hdl\-.\-handle\-.\-net/1926/1374.  
   \citemnobullet  Tustison NJ,  Awate SP, Gee JC:  A Novel Information-Theoretic Point-Set Measure Based on the Jensen-Havrda-Charvat-Tsallis Divergence,   {\em Insight Journal} 2008, http:\-//hdl\-.\-handle\-.\-net/1926/1497.  
   \citemnobullet  Tustison NJ,  Siqueira M, Gee JC: Well-Composedness and the Topological Repairing of 2-D and 3-D Digital Images,   {\em Insight Journal} 2007, http:\-//hdl\-.\-handle\-.\-net/1926/470.  
   \citemnobullet  Tustison NJ,  Gee JC:  Go-Go Gabor Gadgetry,   {\em Insight Journal} 2007, http:\-//hdl\-.\-handle\-.\-net/1926/500 ({\em accepted into the Insight Toolkit}).  
   \citemnobullet   Tustison NJ,  Avants BB, Gee JC: Gridding Graphic Graticules,   {\em Insight Journal} 2007, http:\-//hdl\-.\-handle\-.\-net/1926/475  ({\em accepted into the Insight Toolkit}). 
   \citemnobullet Tustison NJ, Siqueira M, Gee JC: $N$-D linear time exact signed Euclidean distance transform. {\em Insight Journal} 2006, http:\-//hdl\-.\-handle\-.\-net/1926/171 ({\em accepted into the Insight Toolkit}).
   \citemnobullet  Tustison NJ,  Gee JC:  $N$-D $C^k$ B-Spline Scattered Data Approximation,   {\em Insight Journal} 2005, 
   http:\-//hdl\-.\-handle\-.\-net/1926/140 
   ({\em accepted into the Insight Toolkit}).  
   \end{itemize}
 

\end{category}   


% -------- References --------------------------------------------

\begin{category}{References}
\citemnobullet Dr. James C. Gee\\
Associate Professor of Radiologic Science in Radiology\\
Director: Penn Image Computing and Science Laboratory\\
University of Pennsylvania \\
T: (215) 662-7109 \\
james.gee@uphs.upenn.edu
\citemnobullet Dr. Amir A. Amini\\
Professor and Endowed Chair in Bioimaging \\
Director: Medical Image Computing Laboratory\\
University of Louisville \\
T:  (502) 852-4767\\
amir.amini@louisville.edu
\citemnobullet Dr. James R. Brookeman	\\
Professor of Radiology of Biomedical Engineering\\
University of Virginia \\
T:  (434) 243-4969\\
jrb5m@virginia.edu
\citemnobullet Dr. Talissa A. Altes\\
Associate Professor of Radiology \\
Section Head of Pediatric Radiology\\
University of Virginia \\
T:  (434) 982-6018\\
taa2c@virginia.edu

\end{category}

\end{document}
