\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
    \setmainfont{Georgia}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{}
  \pretitle{\vspace{\droptitle}}
  \posttitle{}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage[font={small},labelfont=bf,labelsep=colon]{caption}
\linespread{1.05}
\usepackage[compact]{titlesec}
\usepackage{enumitem}
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
\setlist{nolistsep}
\titlespacing{\section}{2pt}{*0}{*0}
\titlespacing{\subsection}{2pt}{*0}{*0}
\titlespacing{\subsubsection}{2pt}{*0}{*0}
\setlength{\parskip}{6pt}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle

\pagenumbering{gobble}

\section{Personal Statement}\label{personal-statement}

\emph{Nicholas J. Tustison, DSc}

I am a data scientist specializing in medical image analysis with
technical expertise and international recognition in the development of
high-quality, open-source computational strategies for clinically
oriented research. Ever since returning to the University of Virginia in
2010, I have been the lead technical scientist for multiple projects
charged with the development and deployment of computational techniques
for image-oriented studies.

Following my undergraduate studies in physics and computer science, I
completed master's and doctoral degrees in biomedical engineering from
the University of Virginia and Washington University in Saint Louis,
respectively, where my work included the development of mathematical
models for quantification of lung and cardiac imaging biomarkers. I
continued my post-graduate education at the University of Pennsylvania
under the direction of Dr.~James C. Gee, a pioneer in the area of
medical image registration. While at the University of Pennsylvania, my
colleague, Dr.~Brian B. Avants, and I began development of the Advanced
Normalization Tools (ANTs)---a software package which has become one of
the most widely used toolkits in the field for imaging data munging and
analysis. These contributions complement my many other software and
algorithmic inclusions in the Insight Toolkit ---the largest
open-source, medical image analysis software package in the world with
origins linked to the Visible Human Project.

Since all too often ``papers are simply advertisements for the
science,'' my colleagues and I have participated in several unbiased
competitions in order to properly evaluate our work. For example, the
ANTs-based Symmetric Normalization (SyN) image registration framework
has been independently deemed to be a top-performing algorithm for
brain, lung, and cardiac image normalization (in addition to being one
of the only algorithms that can be labeled as true ``open-source''). In
2013 my colleagues and I won an international competition in Nagoya,
Japan for automatically segmenting brain tumors from multi-modal MRI.
Most recently, in 2015, my colleagues and I developed a complete
pipeline for extracting cortical thickness in the brain which has since
been adopted by several research groups. These measures are extremely
salient in identifying neurodegeneration in diseases such as Alzheimers
and other conditions which affect brain development.

Given my role in the development of such widely used data science
approaches, I have given numerous tutorials at various conferences and
to such recognized groups as the Laboratory of NeuroImaging (LONI) at
the University of Southern California and the Montreal Neurological
Institute associated with McGill University. This has led to an
expansion of my circle of collaborators beyond the University of
Virginia to include a joint appointment at the University of California,
Irvine and a pending appointment at the University of Pennsylvania.

I am honored to be affiliated with the University of Virginia and feel
extremely fortunate to work with its high quality faculty in exploring
interesting research questions. I look forward to pursuing my career
path at UVa where I plan to continue focusing on innovations related to
computational medical image analysis and offering crucial expertise in
for imaging data science.

\end{document}
