\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
    \setmainfont{Georgia}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{}
  \pretitle{\vspace{\droptitle}}
  \posttitle{}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage[font={small},labelfont=bf,labelsep=colon]{caption}
\linespread{1.0}
\usepackage[compact]{titlesec}
\usepackage{enumitem}
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
\setlist{nolistsep}
\titlespacing{\section}{2pt}{*0}{*0}
\titlespacing{\subsection}{2pt}{*0}{*0}
\titlespacing{\subsubsection}{2pt}{*0}{*0}
\setlength{\parskip}{3pt}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle

\pagenumbering{gobble}

\section{Personal Statement}\label{personal-statement}

\emph{Nicholas J. Tustison, DSc}

I am a data scientist specializing in medical image analysis with
technical expertise and international recognition in the development of
high-quality, open-source software with targeted application in clinical
areas such as neuro, pulmonary, and cardiac imaging research. Ever since
returning to the University of Virginia in 2010, I have been the lead
technical scientist for various projects in multiple departments across
multiple institutions charged with the development and deployment of
computational techniques for generating salient imaging biomarkers in
small- and large-scale studies.

Following my undergraduate studies in physics and computer science, I
completed master's and doctoral degrees in biomedical engineering from
the University of Virginia and Washington University in Saint Louis,
respectively, where my work included the development of mathematical
models for quantification of lung and cardiac imaging biomarkers.
Following my graduate training, I continued my post-graduate education
at the University of Pennsylvania under the direction of Dr.~James C.
Gee, a technical pioneer in the area of medical image registration.
While at the University of Pennsylvania, my colleague, Dr.~Brian B.
Avants, and I began development of the Advanced Normalization Tools
(ANTs)---a software package which has since become one of the most
widely used toolkits in the field for imaging processing and analysis.\\
Not only is it used by many premier academic research groups, including
widespread use in various departments at the University of Virginia,
but, due to its open-source nature, companies such as General Electric
(G.E.) and International Business Machines (I.B.M.) also employ ANTs.
These contributions to the field complement my many other software and
algorithmic inclusions in the Insight Toolkit ---the largest
open-source, medical image analysis software package in the world with
origins linked to the Visible Human Project and supported by the
National Library of Medicine of the National Institutes of Health with
significant investments on the part of both industrial and academic
institutions. In fact, I am one of the top contributors in terms of new
software modules having recently been part of the team which completely
refactored the image registration framework.

Since all too often in our field ``papers are simply advertisements for
the science,'' my colleagues and I have participated in several unbiased
competitions in order to properly evaluate our data science approaches.
For example, the ANTs-based Symmetric Normalization (SyN) image
registration framework was deemed independently to be the top-performing
algorithm for both brain and lung image normalization in addition to
being the only algorithm that not only is publicly available but
available for uses beyond strictly research. In 2013 my colleagues and I
won an international competition in Nagoya, Japan for automatically
segmenting brain tumor tissue from multi-modal MRI. The machine learning
technique that we developed for the competition has since been used by
several other groups in addition to our generation of new technology for
segmenting cohorts with white matter lesions associated with multiple
sclerosis and white matter hyperintensities associated with traumatic
brain injury. In 2014, we won the best paper award for cardiac motion
correction. Most recently, in 2015, my colleagues and I published and
provided to the public a complete pipeline for extracting cortical
thickness measures in the brain from MRI which was shown to outperform
the only other such available approach, viz., the well-known FreeSurfer
package of Harvard University. Such measures are extremely salient in
identifying neurodegeneration in diseases such as Alzheimers and other
conditions which affect brain development.

Given my role in the development of such widely used data science
approaches, I have given numerous tutorials at various conferences and
to such recognized groups as the Laboratory of NeuroImaging (LONI) at
the University of Southern California and the Montreal Neurological
Institute associated with McGill University. This has led to an
expansion of my circle of collaborators beyond the University of
Virginia to include a joint appointment at the University of California,
Irvine and a pending appointment at the University of Pennsylvania.

I am honored to be affiliated with the University of Virginia and feel
extremely fortunate to work with its high quality faculty in exploring
interesting research questions. I look forward to continuing my career
path at UVa where I plan to continue focusing on innovations related to
computational medical image analysis and offering crucial expertise in
for imaging data science.

\end{document}
